---
title: "How to use `oilPrep` package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use `oilPrep` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `oilPrep` package is inspired by the `recipe` package which does a series of data pre-processing for the oil data set in the `gamlss` package.


Load the package and oil data set.

```{r setup}

# install oilPrep if you haven't
# devtools::install_github("mohowu/oilPrep", build_vignettes = TRUE)

library(oilPrep)
library(gamlss)
data(oil)
```

First we create a `rec` object where we specify what data and response variable to use.

```{r}

rec0 <- rec(oil, "OILPRICE")

```

The `rec0` object contains:

 * `data`: a data frame containing data with transformed values.
 * `meta`: a data frame containing meta data such as what transformations have been done to the data and in what order. It also contains some statistical tests results (p-values for normality and stationarity tests). And finally the correaltion coefficient with the response variable.
 * `y`: The name of the response variable.
 
```{r}

head(rec0$data)

```

```{r}

rec0$meta

```

No meta information yet as no transformations have been done.

```{r}

rec0$y
```

Then we can specify the data transformation we want by using the `step_*` functions.

```{r}

rec1 <- rec0 %>% 
  step_roll("CL2_log", "CL2_log_roll_mean_5", "mean", 5) %>% 
  step_roll("CL2_log", "CL2_log_roll_sd_5", "sd", 5) %>% 
  step_shift("CL2_log", "CL2_log_lag_2", "lag", 2) %>% 
  step_shift("CL2_log", "CL2_log_lead_2", "lead", 2) %>% 
  step_diff("CL2_log", "CL2_log_diff") %>%
  step_two(c("CL2_log", "CL3_log"), "CL2_3_log_spread", "spread") %>% 
  step_two(c("CL2_log", "CL3_log"), "CL2_3_log_ratio", "ratio") %>% 
  step_two(c("CL2_log", "CL3_log"), "CL2_3_log_prod", "product") 
  

```

To get the transformed data.

```{r}

head(rec1$data, 10)
```


To get the meta data.

```{r}

rec1$meta

```


